|

### 2021-02-23 appendix/appendix.Rmd
small edits to appendix

---
title: |
       | Supplementary Materials for "Financial Incentives and Healthcare Provision: Evidence from an Experimental \textit{Aedes aegypti} Control Programme in Brazil"
author:
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

Consider the following interaction between healthcare workers and a government agency.\footnote{This model was inspired by @bolton2005contract and @itoh1991incentives. Here we present a particular case of their model to illustrate the effects of our treatment.} The agency hires the workers to provide preventive healthcare. And the workers decide the amount of effort they will exert, conditional on the compensation scheme they receive.

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{../figures/figrev.pdf}
\caption{Governmental Agency's Revenue in terms of Contract and Compensation}
\label{figrevmax}
\end{figure}

@@

1. There is a 10.3\% effect on the full data model.
2. The coefficient for the other windows are not significant but the signs are consistent with lower disease incidence.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{../figures/rvWorkArea.png}
\caption{Example Working Area.\label{appcevwbl}}
\end{figure}

>>>>

---
title: |
       | Supplementary Materials for "Financial Incentives and Healthcare Provision: Evidence from an Experimental \textit{Aedes aegypti} Control Programme in Brazil"
author:
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: "../manuscript/references.bib"
biblio-style: apalike
always_allow_html: true
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

Consider the following interaction between healthcare workers and a government agency.\footnote{This model was inspired by \citet{bolton2005contract} and \citet{itoh1991incentives}. Here we present a particular case of their model to illustrate the effects of our treatment.} The agency hires the workers to provide preventive healthcare. And the workers decide the amount of effort they will exert, conditional on the compensation scheme they receive.

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{../figures/figrev.pdf}
\caption{Governmental Agency's Revenue in Terms of Contract and Compensation}
\label{figrevmax}
\end{figure}

@@

1. There is a 10.3% effect on the full data model.
2. The coefficient for the other windows are not significant but the signs are consistent with lower disease incidence.

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{../figures/rvWorkArea.png}
\caption{Example Working Area.\label{appcevwa}}
\end{figure}
